How Important are Usage Examples in REST API Documentation?

### 2017-03-06 controlled_study.tex
add the observations + implications

  Observation and Implications
    For each task, describe the results. Provide examples of failed attempts with counts, and relate to the documentation sources to share an observation. Imply what needs to be done.

>>>>

  Key Observations

  API client developers face problem with using the right data type
    Proof: Number of codes in task 2 for G1 vs. G2
    Implication: Example to show a happy path scenario

  API client developers face problem with using the right data format
    Proof: Number of codes in task 3 for G1 vs. G2
    Implication: Example showing expected data format

  API client developers face problem with using request headers
    Proof: Number of codes in task 4 for G1 vs. G2
    Implication: Example showing all 4 inputs

  API client developers face problem with using inter-dependent APIs
    Proof: Number of successful cases on G1. vs. G2
    Implication: Example showing dependency
